Parenting Observation Experiment 2 Lexical Diversity Analysis

### 2019-08-12 parenting_obs_e2/Lexical_Diversity_Analysis.Rmd
fighting papaja

ggplot(ms_lex, aes(x = condition, y = mean, fill = condition)) + 
  ylim(0.0, 0.6)+
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + 
  ylab("TTR") +
  langcog::scale_colour_solarized()  +
  ggthemes::theme_few() 
ggsave(file="figs/e2_TTR.pdf", width=3, height=3)
```

@@

```{r echo=FALSE}
ms_length <- d %>%
  group_by(condition) %>%
  multi_boot_standard(col = "len_sentence")

>>>>

ggplot(ms_lex, aes(x = condition, y = mean, fill = condition)) + 
  ylim(0.0, 0.6) + geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + ylab("TTR") + langcog::scale_colour_solarized() + ggthemes::theme_few() 
ggsave(file="figs/e2_TTR.pdf", width=3, height=3)
```

@@

```{r echo=FALSE}
slen <- lmer(len_sentence ~ condition * age + (1|video), data=d)
summary(slen)

ms_length <- d %>%
  group_by(condition) %>%
  multi_boot_standard(col = "len_sentence")
